Scikit-learn: machine learning without learning the machinery

### 2014-11-07 article.tex
Integrate online learning example
Integrate on-line learning example

@@

% The citation is for "Heaps' law":
% vocabulary size as a function of collection size.
% Gael, feel free to remove it if you think it's too detailed.
With large collections of text, one faces both challenges:
the dimensionality $p$
tends to increase with sample size $n$, as the number of different words used
is greater in large collections \cite[88--89]{manning2009}.
Beyond the mere size of the data matrix
created by a standard vectorization approach, outlined earlier, another challenge
is that the vectorization must be done in two passes over the documents,
as the size of the output vectors is not known up front.
Here, \emph{feature hashing} can be used
to tackle both of these challenges and produce a streaming vectorizer,
the {\tt HashingVectorizer} in scikit-learn.
Words are run through a (stateless) hash function, rather than a lookup table,
to map words to indices.
Collisions may occur, but the hashing algorithm \cite{weinberger2009}
is specially designed to mitigate their effect.
The dimensionality of the output vectors can be set by the user;
the bigger, the less likely collisions will occur.

>>>>

\begin{figure*}[b]
% To have the float on the bottom, we need this declared on the page
% before where it is going to be printed
\lstinputlisting{online_learning_example.py}
\caption{On-line learning example: the main loop iterates through batches
of 1000 documents, vectorizing them on the fly and updating the
classifier. Running the example shows that the error on the test set
progressively decreases as data is accumulated.\label{fig:online}}
\end{figure*}

@@

% The citation is for "Heaps' law":
% vocabulary size as a function of collection size.
% Gael, feel free to remove it if you think it's too detailed.
With large collections of text, one faces both challenges:
the dimensionality $p$
tends to increase with sample size $n$, as the number of different words used
is greater in large collections \cite[88--89]{manning2009}.
Beyond the mere size of the data matrix
created by a standard vectorization approach, outlined earlier, another challenge
is that the vectorization must be done in two passes over the documents,
as the size of the output vectors is not known up front.
Here, \emph{feature hashing} can be used
to tackle both of these challenges and produce a streaming vectorizer,
the {\tt HashingVectorizer} in scikit-learn.
Words are run through a (stateless) hash function, rather than a lookup table,
to map words to indices.
Collisions may occur, but the hashing algorithm \cite{weinberger2009}
is specially designed to mitigate their effect.
The dimensionality of the output vectors can be set by the user;
the bigger, the less likely collisions will occur.
%
A full example doing online learning on a large corpus of text is given
on figure \ref{fig:online}.
